Concurrent Programming with Harmony

### 2020-07-29 book/paper.tex
Updated documentation
Latest

\section*{Exercises}
\begin{problems}
\item Write a new synchronization module, similar to \autoref{fig:spinlocks}, but using
atomic swap (similar to \autoref{ex:swap}).
\item
Run \autoref{fig:incfixed} using (1) \texttt{synch}, (2), \texttt{synchS},
and (3) your own module.  Report how many states were explored by Harmony for each
version of the module.
\item \label{ex:trylock} Implement \texttt{trylock}(\textit{lk}) as an additional
interface for both the \texttt{synch} and \texttt{synchS} modules.
This interface is like \texttt{lock}(\textit{lk}) but never blocks.  It
returns \texttt{True} if the lock was available (and now acquired) or \texttt{False}
if the lock was already taken.
\end{problems}

@@

Harmony supports filtering in \texttt{for loops}.
For example:
\begin{code}
\texttt{for} $i$ in \{ 1..10 \} \texttt{such that} ($i$ \% 2) == 0: ...
\end{code}
\noindent iterates over the even numbers between 1 and 10.

>>>>

\section*{Exercises}
\begin{problems}
\item
Run \autoref{fig:incfixed} using (i) \texttt{synch}, and (ii), \texttt{synchS}.
Report how many states were explored by Harmony for each module.
\item \label{ex:trylock} Implement \texttt{trylock}(\textit{lk}) as an additional
interface for both the \texttt{synch} and \texttt{synchS} modules.
This interface is like \texttt{lock}(\textit{lk}) but never blocks.  It
returns \texttt{True} if the lock was available (and now acquired) or \texttt{False}
if the lock was already taken.
Hint: you do not have to change the existing code.
\end{problems}

@@

Harmony supports nesting and filtering in \texttt{for loops}.
For example:
\begin{code}
\texttt{for} $i$ in \{ 1..10 \}
\texttt{for} $j$ in \{ 1..10 \}
\texttt{such that} $i < j$: ...
\end{code}
